### 2019-02-18 sections/intuition.tex
wording

Several observations can be made of tasks.
One of those is determining the value of a task $\Value(t)$.
Not all tasks have a value, for example the empty editor $\Enter \tau$, which makes $\Value$ a partial function.

@@

In a step $t \Next e$, the decision to move on to e is taken by $\Next$, not by t.
The decision is based on a speculative evaluation of $e$.
The step combinators in $t \Then e$ and $t \Next e$ pass the value $v$ of $t$ to the continuation $e$.
Both steps act like $t$ as long as the step is guarded.
A step is guarded as long as the speculative evaluation $e\ v$ yields $\Fail$.
Once it becomes unguarded, the task continues as $e\ v$.
The task $t \Next e$ requires a continue event $\Continue$ in addition to the step being unguarded.
Speculative evaluation is designed so that it does not have side effects.

The step combinators give rise to a method of internal communication:
They represent data flow that \emph{follows} control flow.

>>>>

Several observations can be made about tasks.
One of those is determining the value of a task $\Value(t)$.
Not all tasks have a value, for example the empty editor $\Enter \tau$, which makes $\Value$ a partial function.

@@

In a step $t \Next e$, the decision to move on is taken by $\Next$, not by $t$.
The decision is based on a speculative evaluation of $e$.
The step combinators in $t \Then e$ and $t \Next e$ pass the value $v$ of $t$ to the continuation $e$.
Both steps act like $t$ as long as the step is guarded.
A step is guarded if either the left task has no value, or the speculative evaluation $e\ v$ yields $\Fail$.
Once it becomes unguarded, the step continues as $e\ v$.
The task $t \Next e$ additionally requires a continue event $\Continue$ to proceed.
Speculative evaluation is designed so that it does not have side effects.

The step combinators give rise to a form of internal communication:
They represent data flow that \emph{follows} control flow.
